\begin{thebibliography}{99}

\bibitem[{\AmS(2004)}]{ams04}
\AmS (2004). \emph{\AmS-\LaTeX{} Version 2 User's Guide} (American Mathematical
  Society, Providence), \url{http://www.ams.org/tex/amslatex.html}.

\bibitem[{Baker and Carter(1972)}]{bake72}
Baker, D.~W. and Carter, N.~L. (1972). \emph{Seismic Velocity Anisotropy
  Calculated for Ultramafic Minerals and Aggregates}, \emph{Geophys.
  Mono.}, Vol.~16 (Am. Geophys. Union), pp. 157--166.

\bibitem[{Benhamou and Colmerauer(1993)}]{benh93}
Benhamou, F. and Colmerauer, A. (eds.) (1993). \emph{Constraint Logic
  Programming, Selected Research} (MIT Press).

\bibitem[{Bestbury(2003)}]{best03}
Bestbury, B.~W. (2003). {$R$}-matrices and the magic square, \emph{J.
  Phys. A} \textbf{36}, 7, pp. 1947--1959.

\bibitem[{Brown(1988)}]{brow88}
Brown, M.~E. (1988). \emph{An interactive environment for literate
  programming}, Ph.D. thesis, Texas A\&M University, TX, USA.

\bibitem[{Churchill and Brown(1990)}]{chur90}
Churchill, R.~V. and Brown, J.~W. (1990). \emph{Complex {V}ariables and
  {A}pplications}, 5th edn. (McGraw-Hill).

\bibitem[{Davidsen(1993)}]{davi93}
Davidsen, B. (1993). Netpbm,
  \url{ftp://ftp.wustl.edu/graphics/graphics/packages/NetPBM}.

\bibitem[{Deligne and Gross(2002)}]{pier02}
Deligne, P.~X. and Gross, B.~H. (2002). On the exceptional series, and
  its descendants, \emph{C. R. Math. Acad. Sci. Paris} \textbf{335}, 11, pp.
  877--881.

\bibitem[{Gupta and Senturia(1997)}]{gupt97}
Gupta, R.~K. and Senturia, S.~D. (1997). Pull-in time dynamics as a
  measure of absolute pressure, in \emph{Proc. IEEE Int. Workshop
  on Microelectromechanical Systems (MEMS'97)} (Nagoya, Japan), pp. 290--294.

\bibitem[{Heard \emph{et~al.}(1994)Heard, Borg, Carter and Raleigh}]{hear94}
Heard, H.~C., Borg, I.~V., Carter, N.~L. and Raleigh, C.~B. (1994).
  {VoQS: Voice Quality Symbols}, Revised to 1994.

\bibitem[{Hobby(1992)}]{hobb92}
Hobby, J.~D. (1992). {A User's Manual for MetaPost}, Tech. Rep. 162,
  AT\&T Bell Laboratories, Murray Hill, New Jersey.

\bibitem[{Jarlskog(1988)}]{jarl88}
Jarlskog, C. (1988). \emph{CP {V}iolation} (World Scientific, Singapore).

\bibitem[{Jones(1973)}]{dani73}
Jones, D. (1973). {The term `phoneme'}, in W.~E. Jones and J.~Laver
  (eds.), \emph{Phonetics in Linguistics: A Book of Reading} (Longman, London),
  pp. 187--204.

\bibitem[{Kernighan(1984)}]{bria84}
Kernighan, B.~W. (1984). {PIC}---{A} graphics language for
  typesetting, Computing Science Technical Report 116, AT\&T Bell
  Laboratories, Murray Hill, New Jersey.

\bibitem[{Lamport(1987)}]{lamp87}
Lamport, L. (1987). \emph{Make Index: An Index Processor For LaTeX}.

\bibitem[{Lamport(1994)}]{lamp94}
Lamport, L. (1994). \emph{\LaTeX, A Document Preparation System}, 2nd edn.
  (Addison-Wesley, Reading, MA).

\bibitem[{Landsberg and Manivel(2002)}]{jame02}
Landsberg, J.~M. and Manivel, L. (2002). Triality, exceptional {L}ie
  algebras and {D}eligne dimension formulas, \emph{Adv. Math.} \textbf{171},
  1, pp. 59--85, \url{http://www.url.com/triality.html}.

\bibitem[{Lodha(1974)}]{lodh74}
Lodha, G.~S. (1974). \emph{Quantitative interpretation of ariborne
  electromagnetic response for a spherical model}, Master's thesis, University
  of Toronto, Canada.

\bibitem[{Richardson(1960)}]{rich60}
Richardson, L.~F. (1960). \emph{Arms and {I}nsecurity} (Boxwood, Pittsburg).

\bibitem[{Weiss(1994)}]{weis94}
Weiss, G.~H. (ed.) (1994). \emph{Contemporary {P}roblems in {S}tatistical
  {P}hysics} (SIAM, Philadelphia).

\end{thebibliography}
